---
title: "Project Name"
author: "Author Name"
pi: "PI name"
date: "`r format(Sys.time(), '%B %d, %Y')`"
footer_message: "Message to follow your name in footer."
# runtime: shiny
output: 
  wcmtheme::wcm_html: 
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  message = FALSE, 
  warning = FALSE)

library(dplyr)
library(dplyr)
library(readr)
library(survival)
library(survminer)
library(gtsummary)

dat_lmtp <- read_rds(here::here("C:/Users/da.salazarb/Documents/data/derived/dat_final_deathAsOutcome.rds")) %>%
  mutate(I_00 = ifelse(I_00 == 0, 1, I_00)) %>% 
  select(-ckd_or_esrd, -hypoxia_ed, ## 1 class
         -ethnicity_missing, -race_missing) %>% 
  tidyr::gather(key="Race", value = "value_race", race_asian, race_black, race_other, race_white, race_miss) %>%
  filter(value_race != 0) %>%
  tidyr::gather(key="Ethnicity", value = "value_ethcnicity", ethnicity_hispanic_or_latino_or_spanish_origin,
                ethnicity_not_hispanic_or_latino_or_spanish_origin, ethnicity_miss) %>% 
  filter(value_ethcnicity != 0) %>% 
  tidyr::gather(key="Hypoxia", value = "value_hypoxia", hypoxia_ed_method_mechanical_ventilation, hypoxia_ed_method_nasal_cannula,
                hypoxia_ed_method_non_rebreather, hypoxia_ed_method_high_flow_nasal_cannula, hypoxia_ed_method_niv_bipap_cpap, 
                hypoxia_ed_method_none, hypoxia_ed_method_venti_mask, hypoxia_ed_method_na) %>% 
  filter(value_hypoxia != 0) %>% 
  tidyr::gather(key="Smoking", value = "value_smoker", smoking_former_smoker, smoking_no, smoking_active_smoker) %>% 
  filter(value_smoker != 0) %>% 
  # mutate(home_o2 = home_o2_yn + (home_o2_miss * 2)) %>% 
  # tidyr::gather(key="home_o2", value = "value_home_o2", home_o2_yn, home_o2_miss) %>% 
  # filter(home_o2 != 0) %>% 
  select(-value_race, -value_ethcnicity, -value_hypoxia, -value_smoker, -home_o2_miss) %>% 
  mutate(Race = case_when(Race == "race_asian" ~ "Asian", 
                          Race == "race_black" ~ "Black", 
                          Race == "race_white" ~ "White", 
                          Race == "race_other" ~ "Other", 
                          Race == "race_miss" ~ "Missing value"),
         Ethnicity = case_when(Ethnicity == "ethnicity_hispanic_or_latino_or_spanish_origin" ~ "Hispanic/Latino/Spanish", 
                               Ethnicity == "ethnicity_not_hispanic_or_latino_or_spanish_origin" ~ "No Hispanic/Latino/Spanish", 
                               Ethnicity == "ethnicity_miss" ~ "Missing value"), 
         Hypoxia = case_when(Hypoxia == "hypoxia_ed_method_mechanical_ventilation" ~ "Mechanical ventilation", 
                             Hypoxia == "hypoxia_ed_method_nasal_cannula" ~ "Nasal cannula",
                             Hypoxia == "hypoxia_ed_method_non_rebreather" ~ "Non rebreather", 
                             Hypoxia == "hypoxia_ed_method_high_flow_nasal_cannula" ~ "High flow nasal cannula", 
                             Hypoxia == "hypoxia_ed_method_niv_bipap_cpap" ~ "Niv bivap cpap", 
                             Hypoxia == "hypoxia_ed_method_venti_mask" ~ "Venti mask", 
                             Hypoxia == "hypoxia_ed_method_none" ~ "None"), 
         Smoking = case_when(Smoking == "smoking_former_smoker" ~ "Former smoker", 
                             Smoking == "smoking_active_smoker" ~ "Active smoker",
                             Smoking == "smoking_no" ~ "No smoker"), 
         home_o2_yn = case_when(home_o2_yn == 0 ~ "No home o2", 
                             home_o2_yn == 1 ~ "Home o2"), 
         Event = case_when(event == 0 ~ "No death", 
                           event == 1 ~ "Death"), 
         sex = case_when(sex == 1 ~ "Male", 
                         sex == 0 ~ "Female"), 
         red_cap_source = case_when(red_cap_source == 1 ~ "East", 
                                    red_cap_source == 0 ~ "Queens")
         ) %>% 
  rename(Age = age, Sex = sex, Hypertension = htn, Cirrhosis = cirrhosis, Asthma = asthma, Immunosuppression = immunosuppressed)
```

> Inspired by the better poster, try including a take-home message about the report.

# Reasearch question

***What is the effect of invasive mechanical ventilation (IMV) on overall survival among COVID-19 patients?***

# Study design

![Study design. (A) For 3323 COVID-19 patients, hospitalization records were used for 14 days, starting from the day of hospitalization. Time-dependent variables are L, A, C and Y which were recorded daily. Baseline variables (Bs) contain sociodemographic and comorbidities variables. (B) Two contrasting scenarios correspond to subjects exposed to oxygen supplementation or none at all. On the other hand, the modified treatment policy is a more conservative strategy that avoids the provision of IMV. In both scenarios, the outcome corresponds to death.](G:/Mi unidad/Tutorial_2018-10/10_WCM/covid/results_design.jpg)

# Results

## Data description

The following graphs and tables are presented below:

-   **Sociodemographic**: summary of sociodemographic variables separated by patients who presented the event and those who did not in the 14-day period.

-   **Comorbidities**: summary of comorbiditiy variables separated by patients who presented the event and those who did not in the 14-day period.

-   **Kaplan-Meier plot**

## 

# Tabset {.tabset}

## Summary


```{r}
tbl_demo <- dat_lmtp %>% 
  select(Event, red_cap_source, Age, Sex, Race, Ethnicity, bmi, Hypoxia, home_o2_yn, Smoking)

tbl_demo %>% 
  tbl_summary(by = Event, 
              label = list(bmi ~ "Body mass index", 
                           home_o2_yn ~ "Home oxygen status", 
                           red_cap_source ~ "Data source")) %>% 
  add_p() %>%
  bold_labels() %>%
  add_overall() %>%
  # add_n() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Outcome**")
```

## Comorbidities

```{r}
tbl_comorb <- dat_lmtp %>% 
  select(Event, Hypertension, cva, dm, cad, active_cancer, Cirrhosis, Asthma, copd, ild, hiv, Immunosuppression)

tbl_comorb %>% 
  tbl_summary(by = Event, 
              label = list(dm ~ "Diabetes mellitus", 
                           cad ~ "Coronary artery disease", 
                           cva ~ "Cerebrovascular accident",
                           copd ~ "Chronic obstructive pulmonary disease", 
                           active_cancer ~ "Active cancer", 
                           ild ~ "Interstitial lung Disease", 
                           hiv ~ "HIV infection")) %>% 
  add_p() %>%
  bold_labels() %>%
  add_overall() %>%
  # add_n() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_spanning_header(c("stat_1", "stat_2") ~ "**Outcome**")
```

## Kaplan-Meier plot

```{r}
ggsurvplot(
  fit = survfit(Surv(fu, event) ~ 1,
                data = dat_lmtp %>% 
                  mutate(event = ifelse(fu > 14, 0, event), fu = ifelse(fu >14, 14, fu)) %>% 
                  select(fu, event)),
  xlab = "Days", 
  ylab = "Overall survival probability", 
  risk.table = TRUE, risk.table.fontsize = 3, 
  break.time.by = 1, xlim = c(0,14), ylim = c(0.5,1),
  legend.labs =
    c("Patients"), 
  ggtheme = theme_light(
    base_size = 12,
    base_family = "",
    base_line_size = 11/22,
    base_rect_size = 11/22
  ))
```

<!-- ## Table day i -->

<!-- Hola Mundo -->

<!-- ```{r} -->

<!-- dat_lmtp %>% select(ends_with("_13")) %>% -->

<!--   tbl_summary(by = "Y_13") -->

<!-- ``` -->
